Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-23 paper/manuscript.tex
full draft of Discussion

Overall, we have described a new hybrid experimental-analytical approach to quantify antigenic effects.
Useful both for characterizing the epitopes and escape mutants for single antibodies, but more importantly for comparing across antibodies.
As antibodies are increasingly considered for anti-viral therapeutics, the ability to comprehensively quantify the potential for viral escape will be useful

>>>>

A major rationale for studying broadly neutralizing antibodies is that they are hoped to be more resistant to viral evolutionary escape than the antibodies that dominate natural immune responses to influenza virus~\citep{krammer2015advances,corti2017tackling}.
We have used a new approach to quantify the extent to which this is actually true, and shown that anti-viral activity of broad anti-stalk antibodies is indeed more -- although certainly not completely -- resistant to erosion by viral point mutations.
Going forward, we suggest that quantifying the ease of viral escape will be a useful complement to more traditional techniques that characterize the structural epitopes and strain breadth of anti-viral antibodies.
